---
title: "imageRy"
author: "Duccio Rocchini, Giovanni Nocera, Elisa Thouverai"
date: "2023-07-05"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

The imageRy R package has been thought to speed up teaching activities, avoiding import/export processes of imagery, providing a catalogue of different imagery coming out from the [Earth Observatory](https://earthobservatory.nasa.gov/) site of the NASA, as well as from analysed Sentinel-2 data.

> **Note**
> In order to install the package you might refer to GitHub by the devtools package as:

```{r, eval=FALSE}
devtools::install_github("ducciorocchini/imageRy")
```

> **Note**
Need a guide about devtools? [Here](https://cran.r-project.org/web/packages/githubinstall/vignettes/githubinstall.html) it is.

## Including plots from the imageRy R package

Once the imageRy R package has been installed the data are ready available-

```{r}
library(imageRy)
data(duccio)
```

The list of data is available [here](https://github.com/ducciorocchini/imageRy/tree/main/data).


```{r, warning=FALSE}
library(raster)
plotRGB(duccio, 1, 2, 3, stretch="lin")
```
